### 2024-02-04 inst/scripts/testDemo.Rmd
extend demographic exploration

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=ki,km=km,traits=a,coordinates=pos,G=100,plot=T,sizes=c(50))
initcomus$occupation[,]=1
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(K*50,age="random",community = communities),(K*50,2))
newtestres=modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time"),ma=1,traitsid=paste0("t",1:2),F_Th = 70)
table(newtestres$population[,"community"])
population=newtestres$population
rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))
population=resetIds(population)

traitsid=paste0("t",1:2)
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=100,plot=T)
initcomus$size=unname(table(population[,"community"]))
library(parallel)
bs=round(runif(200,.3,.44),digit=3)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsizesonly=parSapply(cl,bs,function(b){
           modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=generatePathways(z=2),age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F)$popsize
})
stopCluster(cl)
saveRDS(file="pposizeLargerTh.RDS",allpopsizesonly)
par(mfrow=c(1,3))
boxplot(lengths(allpopsiz)~bs,ylab="simu length vs birth rate ",xlab="birth rate",main="extinctions")
finished=allpopsiz[lengths(allpopsiz)==500]
finsize=sapply(finished,"[",500)
boxplot(finsize~bs[lengths(allpopsiz)==500],ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end without extinctions")
abline(h=nrow(smallpop),col="red")

allfinal=sapply(allpopsiz,function(i)i[length(i)])
boxplot(allfinal~bs,ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end ")
abline(h=nrow(population),col="red")

plot(allpopsiz[[1]],xlim=c(0,500),ylim=c(0,800))
compressedts=sapply(1:500,function(t)sapply(allpopsiz,function(i)i[t]))
getdist=apply(compressedts,2,quantile)

>>>>

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=ki,km=km,traits=a,coordinates=pos,G=100,plot=T,sizes=c(50))
initcomus$occupation[,]=1
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(K*percomu,age="random",community = communities),generateTraitsMatrix(K*50,2))
newtestres=modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time"),ma=1,traitsid=paste0("t",1:2),F_Th = 70)
table(newtestres$population[,"community"])
population=newtestres$population
rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))
population=resetIds(population)

traitsid=paste0("t",1:2)
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=10)
a=initAdaptiveTraits(ki=ki,km=km,n=3 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T)
initcomus$size=unname(table(population[,"community"]))
#initcomus$adaptivetraits[3,]=1
library(parallel)
population=cbind(population[,1:9],generateTraitsMatrix(nrow(population),24))
expname="NeutrEvoLSingleBR2kRHO_1_limited"
dir.create(expname)
traitsid=paste0("t",1:24)
population[,traitsid]=0
population[population[,"community"]==1,traitsid]=1
population[population[,"community"]==2,traitsid]=1
bs=round(runif(300,.338,.345),digit=4)
cl<-makeCluster(40,type="FORK",outfile=file.path(expname,"log.txt"))
allpopsizesonly=parSapply(cl,1:200,function(b){
                              set.seed(as.numeric(Sys.time())+b)
                              tryCatch({
           singlesimu=modelVector(K=K, m=1, b=0.348, r=0, rho=1, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=2000, tp=neutraltraitsParam,age.threshold=20, out=c("popsize","finalpop","finalcomus","traitsumary","popsumary","deaths","births","repros"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F)
           saveRDS(file=file.path(expname,paste0("singlesimu_s_",b,".RDS")),singlesimu)
           singlesimu$popsize
                              },error=function(e){ print("problem ======");print(e)})
})
stopCluster(cl)
saveRDS(file=file.path(expname,"neutralTraits_longer.RDS"),allpopsizesonly)

expname="AdapEvoLSingleBR5kRHO_1"
cl<-makeCluster(40,type="FORK",outfile=file.path(expname,"log.txt"))
initcomus$adaptivetraits[c(3,6),]=1
allpopsizesonly=parSapply(cl,1:80,function(b){
                              set.seed(as.numeric(Sys.time())+b)
                              tryCatch({
           singlesimu=modelVector(K=K, m=1, b=0.348, r=0.05, rho=1, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("popsize","finalpop","finalcomus","traitsumary","popsumary","deaths","births","repros"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F,beta=-1)
           saveRDS(file=file.path(expname,paste0("singlesimu_s_",b,".RDS")),singlesimu)
           singlesimu$popsize
                              },error=function(e){ print("problem ======");print(e)})
})
stopCluster(cl)
saveRDS(file=file.path(expname,"neutralTraits_longer.RDS"),allpopsizesonly)
expname="AdapEvoLSingleBR5kRHO_1_longer"
cl<-makeCluster(40,type="FORK",outfile=file.path(expname,"log.txt"))
allpopsizesonly2=parSapply(cl,1:200,function(b){
                              set.seed(as.numeric(Sys.time())+b)
                              tryCatch({
           singlesimu=modelVector(K=K, m=1, b=0.348, r=0.02, rho=1, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=2000, tp=neutraltraitsParam,age.threshold=20, out=c("popsize","finalpop","finalcomus","traitsumary","popsumary","deaths","births","repros"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F)
           saveRDS(file=file.path(expname,paste0("singlesimu_s_",b+80,".RDS")),singlesimu)
           singlesimu$popsize
                              },error=function(e){ print("problem ======");print(e)})
})
stopCluster(cl)
saveRDS(file=file.path(expname,"neutralTraits_longer2.RDS"),allpopsizesonly)
plot(allpopsiz[[1]],xlim=c(0,500),ylim=range(compressedts))
compressedts=sapply(1:500,function(t)sapply(allpopsizesonly[lengths(allpopsizesonly)>2],function(i)i[t]))
getdist=apply(compressedts,2,quantile,na.rm=T)
